The Topic Browser\\An Interactive Tool for Browsing Topic Models

### 2010-10-21 masters_thesis/tool_nips_workshop/paper.tex
Editing on the tool paper from feedback, and I put in some screenshot images for the paper

Topic models have been shown to be very useful for capturing a measure of
semantic meaning in a corpus.  Many individualized and cherry-picked
visualizations of topic models have been done, showing the potential of topic
models to give valuable insight into a corpus.  However, good, general tools
for browsing the entire output of a topic model along with its corpus have been
lacking.  We present an interactive tool that incorporates a significant amount
of prior work in displaying topic models, as well as a few novel ideas that
greatly enhance the visualization of these models.

@@

\section{Introdcution}

Proper visualizations are essential to extracting information from data,
especially large and highly dimensional sets of data.  Large text corpora are
particularly difficult to visualize, as they typically include thousands of
documents and perhaps millions of words.  Topic
modeling~\cite{blei-2003-latent-dirichlet-allocation} is a method of reducing
the dimensionality of a corpus into a set of meaningful topics.  Topic models
have been used with some success as an aid to corpus
visualization~\cite{blei-2009-topic-models,
newman-2010-visualizing-with-topic-maps}.  However, in general the presentation
of topic models has been limited to hand selected topics that show the model in
the best light possible.  These presentations leave the viewer wondering what
else the topic model discovered and provide little help in gaining a deep
understanding of the model.

To aid in the visualization of topic models, we present The Topic Browser, a
tool for interactively exploring both the output of a topic modeling algorithm
and its attendant corpus.  Our topic browser incorporates many visualizations
of topic models previously published, as well as some innovative ideas of our
own.  The Topic Browser is an aid both to those who wish to browse through a
corpus and for those who wish to analyze the topic model itself.

The rest of this paper simply describes the Topic Browser.  We demonstrate our
tool with a topic model run on a collection of about 460 campaign speeches from
the 2008 presidential primary and general election.

@@

Aside from the documents and the topic model themselves, our browser
incorporates three other pieces of information: attributes, or metadata,
associated with each document, topic metrics, and document metrics.  Here we
give a brief description of these kinds of information, deferring a discussion
of their use in visualization to the following sections.

@@

In order to browse more effectively through topics, we introduce topic metrics
that give information about the topic.  These range from simple metrics, such
as the number of tokens and types labeled with the topic, to more complicated
metrics like how spread out the topic is across documents, or how coherent its
words are~\cite{newman-2010-automatic-evaluation-of-topic-coherence}.  We also
use pairwise topic metrics as similarity measures to show similar topics.

@@

The sidebar in our browser is the main navigation tool.  Apart from the obvious
task of directing the user to various parts of the visualization tool, then
main purpose of the sidebar is to list the items of a particular type (such as
topics or documents).  The new capability that we bring to the of listing the
items is the ability to sort and filter these lists as the user desires.

When presenting the results of topic models, papers will often cherry-pick the
list of topics looking for particularly good topics to display, leaving the
large number of meaningless topics untouched.  While such presentations may
help the researcher to highlight the benefits of her new topic model, they hide
the fact that finding good topics is often a laborious process.  With our topic
and document metrics, the sorting and filtering capabilities of the sidebar
list allow the user to often go quickly to the very topics he desires to find.

@@

Topic models are typically presented as static lists of words, often simply
showing the top ten words from each topic in a list.  While this practice is
often sufficient to give a reader a basic idea of what the topic captured, it
is largely incapable of conveying a deep understanding of the context of that
topic in the corpus.  In order to answer significant questions about a corpus
one must browse the topics discovered, and previous methods have failed to
adequately allow the user to explore topics.  Our visualizer presents new ways
to gather information about a topic in the corpus, both in how the words in the
topic are displayed and in other information that is presented about the topic.

@@

Instead of showing a list of the top ten words, we show a word cloud of the top
100, where the size of each word is determined by the probability of seeing
that word in the topic.  We also show a re-weighted word cloud as determined by
David Blei's Turbo Topics method~\cite{blei-2009-turbo-topics}.  While these
visualizations are modest improvements over typical visualization methods, our
most useful display of the words is showing them in their context.

The topics in a topic model cannot be fully interpreted when completely
separated from their context.  Thus we display the top ten words in the topic
inside of their context.  We select a random token of each word type labeled
with the topic and show up to 50 characters on either side of the token.  We
also allow the user to cycle through contexts to gain a broader view of how
each word is actually used in that topic in the corpus.

@@

We give two main ways of getting more information about topics in the model.
The first is showing documents and attribute values which have the highest
number of tokens labeled with that topic, or the highest percent in the
document or attribute.  This allows the user to quickly find documents that
best demonstrate what the topic captured.  Showing the top values for a given
attribute (such as authors for the attribute ``Author'') gives the user an idea
of how focused the topic is and often gives interesting information about the
corpus being browsed (for example, in Figure \ref{fig:something}, we see that
Democrats spoke more often about education than Republicans did).

@@

In addition to allowing the user to browse the topics in the topic model, we
provide means for browsing the documents, words, and attributes in the corpus.
These facilities give users means to explore the corpus itself in the context
of the topic model.

When simply browsing through the documents, we provide sorting and filtering
methods on the list of documents, as mentioned previously.  When looking at a
particular document, we show basic information about the document, its text,
the topic distribution in the document, and similar documents based on that
distribution.  When looking at the document in the context of a topic, we also
highlight the tokens in the document that were labeled with that topic.  All of
this has been done previously, besides the sorting and filtering of the
documents, and in fact constitutes the entirety of most previous corpus
browsers based on topic models---this functionality is all that is generally
provided.

We also provide views of individual words in the corpus.  When viewing a word
in the context of a topic, the user can see all uses of the word in that topic
in the corpus, with context taken from their corresponding documents.  The user
can also view words independently with a search-like interface, seeing what
topics and what documents in which the word appears most frequently.  While
providing basic functionality, however, the search interface leaves much to be
desired, as only single words can currently be searched for.  We plan on
expanding that to phrases in the future.

The user can also look at aggregated information for values of an attribute
(i.e., a particular author or year in the documents).  This view is also at
present somewhat limited, showing only what topics and words are used most
frequently by the collection of documents with that attribute.

@@

There has been a wide variety of plots used in the visualization of topic
models.  We currently include two kinds of plots in our topic browser, with
plans to implement many more.  The first is showing trends for topics over the
values of an attribute (such as date, or author), useful for corpus browsing.
This kind of plot has been used in visualizing topic models almost since their
introduction~\cite{griffiths-2004-finding-scientific-topics}.  Our topic
browser allows the user to very quickly generate these trend plots over any
topic or combination of topics for any attribute of the documents in the
corpus.

The second kind of plot that we include is more useful for analyzing and
understanding the behavior of the topic model itself.  We allow the user to
plot two topic metrics against each other and compute a linear regression.
This allows the user to see some interesting properties of the topic metrics,
such as the fact that document entropy seems to correlate logarithmically with
the number of tokens in the topic, and that coherence does not seem to
correlate with any other topic metric.  The user can also found outliers, such
as topics with low document entropy but a high token count, that can then be
examined in the topic page.

@@

We have presented the Topic Browser, an interactive tool for browsing both the
output of a topic model and the corpus that was modeled.  We have shown that
our tool incorporates many previously published visualizations of topic models,
including basic corpus browsing functionality, plots of trends over attributes
in the corpus, and Blei's turbo topics method of finding significant phrases
for each topic.  We have also presented many novel ways to get information from
a topic model in an interactive browsing experience.

While our tool is still under development, we intend to make it open and freely
available, both for those wishing to browse through a corpus in the context of
a topic model, and for those wishing to better understand topic models and
develop new models.  Our tool currently supports any topic model that labels
individual tokens in the corpus with a topics.  We have plans to include
special visualizations for more complicated topic models, such as Topics over
Time, sentiment-topic models, and others.

>>>>

Topic models have been shown to capture a measure of the semantics in a corpus.
Many individualized and cherry-picked visualizations of topic models have been
reported in the literature, showing the potential of topic models to give
valuable insight into a corpus.  However, good, general tools for browsing the
entire output of a topic model along with the analyzed corpus have been
lacking.  We present an interactive tool that incorporates both prior work in
displaying topic models as well as some novel ideas that greatly enhance the
visualization of these models.

@@

\section{Introduction}

Proper visualizations are essential to extracting information from and
identifying trends in data, especially large, highly dimensional data.  Large
text corpora are particularly difficult to visualize, as they typically include
thousands of documents and perhaps millions of words.  Topic
modeling~\cite{blei-2003-latent-dirichlet-allocation} is a method of reducing
the dimensionality of a corpus into a set of meaningful topics.  Topic models
have been used with some success as an aid to corpus
visualization~\cite{blei-2009-topic-models,
newman-2010-visualizing-with-topic-maps}.  However, in general the presentation
of topic models has been limited to hand selected topics that show the model in
the best light possible.  These presentations leave the viewer wondering what
else the topic model discovered and provide little help in gaining a deep
understanding of the model.

To aid in the visualization of topic models and in pattern discovery in
document collections, we present The Topic Browser, a tool for interactively
exploring both the output of a topic modeling algorithm and its attendant
corpus.  Our topic browser incorporates many visualizations of topic models
previously published as well as some innovative ideas of our own.  The Topic
Browser is an aid both to those who wish to browse through a corpus and for
those who wish to analyze the topic model itself.

The rest of this paper describes the Topic Browser.  We demonstrate our tool
with a topic model run on a collection of about 460 campaign speeches from the
2008 presidential primary and general elections.

@@

Aside from the documents and the topic model themselves, our browser
incorporates three other pieces of information: attributes (or metadata)
associated with each document, topic metrics, and document metrics.  Here we
give a brief description of these kinds of information, deferring a discussion
of their use in visualization to the subsequent sections.

@@

In order to browse more effectively through topics, we introduce topic metrics
that give information about the topic.  These range from simple metrics, such
as the number of tokens and types labeled with the topic, to more complicated
metrics like how dispersed the topic is across documents, or how coherent its
words are~\cite{newman-2010-automatic-evaluation-of-topic-coherence}.  We also
use pairwise topic metrics as similarity measures to show similar topics.

@@

The sidebar in our browser is the main navigation tool.  Apart from the obvious
task of directing the user to various parts of the visualization tool, the main
purpose of the sidebar is to list the items of a particular type (such as
topics or documents).  The new capability introduced by this browser is the
ability to sort and filter these lists as the user desires.

When presenting the results of a topic model analysis, papers will often
cherry-pick the list of topics looking for particularly good topics to display,
leaving the large number of meaningless topics untouched.  While such
presentations may help the researcher to highlight the benefits of her new
topic model, they hide the fact that finding good topics is often a laborious
process.  With our topic and document metrics, the sorting and filtering
capabilities of the sidebar list allow the user to often go quickly to the very
topics he desires to find.

@@

Topic models are typically presented as static lists of words, often simply
showing the top ten words from each topic in a list.  While this practice is
often sufficient to give a reader a basic idea of what the topic captured, it
is largely incapable of conveying a deep understanding of the context of that
topic in the corpus.  In order to answer significant questions about a corpus
one must browse the topics discovered, and previous methods have failed to
adequately allow the user to explore topics.  Our browser presents new ways
to gather information about a topic in the corpus, both in how the words in the
topic are displayed and in that is presented about the topic.

@@

Instead of showing a list of the top ten words, we show a word cloud of the top
100, where the size of each word is determined by the probability of seeing
that word in the topic.  We also show a re-weighted word cloud as determined by
Blei \& Lafferty's Turbo Topics method~\cite{blei-2009-turbo-topics}.

While these visualizations are modest improvements over typical visualization
methods, our most useful display of the words is showing them in their context.

The topics in a topic model cannot be fully interpreted when completely
separated from their context.  Thus we display the top ten words in the topic
inside of their context.  We select a random token of each word type labeled
with the topic and show up to 50 characters on either side of the token,
keeping words intact.  We also allow the user to cycle through contexts to gain
a broader view of how each word is actually used in that topic in the corpus.

@@

The browser provides two main ways of getting more information about topics in
the model.  The first is showing documents and attribute values which have
either the highest number of tokens labeled with that topic or the highest
proportion (by percentage) of the given topic.  This allows the user to quickly
find documents that best demonstrate what the topic captured.  Showing the top
values for a given attribute (such as authors for the attribute ``Author'')
gives the user an idea of how focused the topic is and often gives interesting
information about the corpus being browsed (for example, in Figure
\ref{fig:something}, we see that Democrats spoke more often about education
than Republicans did, at least in the topic shown).

@@

In addition to enabling the user to browse the topics in the topic model, we
provide means for browsing the documents, words, and attributes in the corpus.
These facilities give users means to explore the corpus itself in the context
of the topic model.

When simply browsing through the documents, we provide sorting and filtering
methods on the list of documents, as mentioned previously.  When looking at a
particular document, we show basic information about the document, its text,
the topic distribution in the document, and similar documents based on that
distribution.  When looking at the document in the context of a topic, we also
highlight the tokens in the document that were labeled with that topic.  All of
this has been done previously, aside from the sorting and filtering of the
documents, and in fact constitutes the entirety of most previous corpus
browsers based on topic models---this functionality is all that is generally
provided.

We also provide views of individual words in the corpus.  When viewing a word
in the context of a topic, the user can see all uses of the word in that topic
in the corpus, with context taken from their corresponding documents.  The user
can also view words independently with a search-like interface, seeing topics
and documents in which the word appears most frequently.  While providing basic
functionality, however, the search interface leaves much to be desired, as only
single words can currently be searched for.  We plan on expanding that to
phrases.

The user can also look at aggregated information for values of an attribute
(i.e., a particular author or year in the documents), combining all of the
topic and word counts for all documents with the given attribute.  This view is
also at present somewhat limited, showing only what topics and words are used
most frequently by the collection of documents with that attribute.

@@

We currently include two kinds of plots in our topic browser, with plans to
implement many more.  The first is showing trends for topics over the values of
an attribute (such as date, or author), useful for corpus browsing.  This kind
of plot has been used in visualizing topic models almost since their
introduction~\cite{griffiths-2004-finding-scientific-topics}.  Our topic
browser allows the user to interactively generate these trend plots over any
attribute for any topic or combination of topics of the documents in the
corpus.

The second kind of plot that we include is more useful for analyzing and
understanding the behavior of the topic model itself.  We allow the user to
plot two topic metrics against each other and compute a linear regression.
This allows the user to see some interesting properties of the topic metrics,
such as the fact that document entropy seems to correlate with the logarithm of
the number of tokens in the topic, and that coherence does not seem to
correlate with any other topic metric.  The user can also find outliers, such
as topics with low document entropy but a high token count, that can then be
examined in the topic page. (TODO: use Obama vs. McCain as example here)

@@

We have presented the Topic Browser, an interactive tool for browsing both the
output of a topic model and the corpus that was modeled.  We have shown that
our tool incorporates many previously published visualizations of topic models,
including basic corpus browsing functionality, plots of trends over attributes
in the corpus, and Blei \& Lafferty's Turbo Topics method of finding
significant phrases for each topic.  We have also presented many novel ways to
mine information from a topical analysis of a corpus in an interactive browsing
experience.

While our tool is still under development, we intend to make it open and freely
available, both for those wishing to browse through a corpus in the context of
a topic model, and for those wishing to better understand topic models and
develop new models.  Our tool currently supports any topic model that labels
individual tokens in the corpus with topics.  We have plans to include special
visualizations for more complicated topic models, such as Topics over Time,
sentiment-topic models, hierarchical topic models, and others.
